Case Study: RNA-Seq Differential Analysis (basal ganglia)

### 2018-03-22 datasets/RNA-Seq/RNAseq-gtex.Rmd
Remove bib from RNAseq-gtex yaml

---
title: "Case Study: RNA-Seq Differential Analysis (basal ganglia)"
author: "Chinmay Shukla, Alejandro Reyes, Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
bibliography: bibliography.bib
---

>>>>

---
title: "Case Study: RNA-Seq Differential Analysis (basal ganglia)"
author: "Chinmay Shukla, Alejandro Reyes, Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---
